Comparing ChatGPT-4 to Physicians for Assigning Causes of Death from Verbal Autopsy: A Case Study of 6939 Deaths in Sierra Leone from 2019-2022

### 2024-02-09 manuscript/manuscript.tex
Add pseudocode from rajeev
Use python instead of java

The ChatGPT-3.5 and ChatGPT-4 Application Programming Interface (API) was accessed using Java and used to assign CODs for each record. ChatGPT-3.5 used the \verb|gpt-3.5-turbo| model, while ChatGPT-4 used the \verb|gpt-4-0613| mode. The parameter \verb|top_p| for ChatGPT-3.5 and ChatGPT-4, representing the sampling temperature, was set to 0.3\footnote{We tested for top\_p values between 0.1 to 0.9 at intervals of 0.1 on five records that did not return outputs from ChatGPT-4 until all five records returned output. At top\_p=0.3, all five records produced output.} to consider only the top 30\% probability mass from the token results \cite{openaiOpenAIPlatformAPI2024}. Higher values closer to 1 may make the results more random, while lower values closer to 0 make the results more focused.

>>>>

The ChatGPT-3.5 and ChatGPT-4 Application Programming Interface (API) was accessed using Python 3.12 and used to assign CODs for each record. ChatGPT-3.5 used the \verb|gpt-3.5-turbo| model, while ChatGPT-4 used the \verb|gpt-4-0613| mode. The parameter \verb|top_p| for ChatGPT-3.5 and ChatGPT-4, representing the sampling temperature, was set to 0.3 to consider only the top 30\% probability mass from the token results \cite{openaiOpenAIPlatformAPI2024}. Higher values closer to 1 may make the results more random, while lower values closer to 0 make the results more focused.
